Bootstrapping Multi-atlas Hippocampal Subfield Segmentation by using Multiple Automatically Generated Templates

### 2013-09-02 paper.Rnw
Added MAGeT schematic, and fixed a table

\begin{abstract}
%Neuroimaging research often relies on automated anatomical segmentations of MR
%images of the brain. Current multi-atlas based approaches provide accurate
%segmentations of brain images by propagating manually derived segmentations of
%specific neuroanatomical structures to unlabelled data. These approaches often
%rely on a large number of such manually segmented atlases that take significant
%time and expertise to produce. We present an algorithm for the automatic
%segmentation of the hippocampus that minimizes the number of atlases needed
%while still achieving similar accuracy to multi-atlas approaches.
\end{abstract}

@@

\begin{figure}
  \caption{The \mb algorithm \label{fig:MAGeT}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Subfield Validation Template library demographics (healthy controls)
%                                     
<<WAval-healthy-demographics, echo=F, results="asis",cache=FALSE>>=
master = read.csv('data/DT_study.csv')
tab <- summary(~Age + Sex + Education + Handedness, 
               data = master, method="reverse", na.rm = TRUE, test=FALSE)
caption = 
  "\\textbf{Subfield validation healthy control demographics.}
  CN     - Cognitively Normal. 
  LMCI   - Late-onset Mild Cognitive Impairment. 
  AD     - Alzheimer's Disease.  
  Hisp   - Hispanic. 
  CDR-SB - Clinical Dementia Rating-Sum of Boxes.  
  ADAS   - Alzheimer's Disease Assessment Scale.  
  MMSE   - Mini-Mental State Examination."
latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=FALSE,
      caption=caption, caption.loc = c("top"),
      title="tab:WAval-healthy-demographics")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{abstract}
Neuroimaging research often relies on automated anatomical segmentations of MR
images of the brain. Current multi-atlas based approaches provide accurate
segmentations of brain images by propagating manually derived segmentations of
specific neuroanatomical structures to unlabelled data. These approaches often
rely on a large number of such manually segmented atlases that take significant
time and expertise to produce. We present an algorithm for the automatic
segmentation of the hippocampus that minimizes the number of atlases needed
while still achieving similar accuracy to multi-atlas approaches.
\end{abstract}

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=\textwidth]{figure/MA-MAGeTBrain-Schematic}
  \end{centering}
  \caption{A schematic illustration of basic multi-atlas segmentation and \mb
  segmentation \label{fig:MAGeT}}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Subfield Validation Template library demographics (healthy controls)
%                                     
<<WAval-healthy-demographics, echo=F, results="asis",cache=FALSE>>=
master = read.csv('data/DT_study.csv')
tab <- summary( Diagnosis ~ Age + Sex + Education + Handedness, data = master,
    method="reverse", na.rm = TRUE, test=FALSE)
caption = 
  "\\textbf{Subfield validation healthy control demographics.}
  CN     - Cognitively Normal. 
  LMCI   - Late-onset Mild Cognitive Impairment. 
  AD     - Alzheimer's Disease.  
  Hisp   - Hispanic. 
  CDR-SB - Clinical Dementia Rating-Sum of Boxes.  
  ADAS   - Alzheimer's Disease Assessment Scale.  
  MMSE   - Mini-Mental State Examination."
latex(tab, file="", size="scriptsize",landscape=FALSE, ctable=FALSE,
      caption=caption, caption.loc = c("top"),
      title="tab:WAval-healthy-demographics")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
